Subjective Experience of Demands and Resources across O*NET Job Elements

### 2024-07-10 Submission.Rmd
Updating the Introduction Section

Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing. Beginning with resources ADD JDR STUFF ON RESOURCES AND MOTIVATION HERE. @kim2020thriving found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a *challenge* was associated with sources of motivation (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing. The opposite occurred when a demand was appraised as a *hindrance* – in those instances, the appraisal had a negative association with motivational resources. @cavanaugh2000empirical, in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern. @chen2021daily found that daily challenge demands were positively related to cognitive wellbeing and work-family enrichment. Daily hindrance demands were negatively related to these outcomes. In contrast, @abbas2019challenge found that challenge and hindrance stressors were *both* positively related to strain and turnover intentions. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with it [@crawford2010linking]. Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety [@rodell2009can]. Lastly, @gerich2017relevance concluded that employee wellbeing was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands. In addition to the studies above, several meta-analyses also support differential associations across a variety of organizational outcomes as well. For example, both challenges and hindrances have been shown to positively predict strain [@lepine2005meta; @podsakoff2007differential; @webster2010toward]. Many other outcomes are differentially related to challenges and hindrances, largely in the expected direction. For example, motivation, job satisfaction, commitment, and performance have been shown to positively relate to challenge stressors and negatively relate to hindrance stressors [@lepine2005meta]. Turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance stressors [@podsakoff2007differential]. @kim2020thriving, similarly, found evidence for the differential results via challenge and hindrance appraisals.

@@

In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain [e.g., @bakker2005job] and burnout [e.g., @xanthopoulou2007job]. BUILD ON THIS - DETAILS OF THESE TWO STUDIES AND MORE - BAKKER 2010

>>>>

Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance [e.g., @lepine2005meta]. We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout. Beginning with resources, @hakanen2008job found job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, @bakker2007job found that resources were most predictive of engagement when job demands were especially high.

The findings regarding demands are more complex, presumably because the way challenge vs. hindrance appraisal influence coping strategies. Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and work meaningful [@chen2021daily], engagement [@crawford2010linking], and strain and turnover intentions [e.g., @abbas2019challenge], for example. Challenge appraisals have been negatively associated with job search behaviors [e.g., @cavanaugh2000empirical].

Hindrance demands (appraisals) are largely related to outcomes as the job demands-resources model predicts. When a demand was appraised as a hindrance – it was negatively associated with motivational resources [@kim2020thriving], engagement [@crawford2010linking], job search behaviors and job satisfaction, [@cavanaugh2000empirical]. @chen2021daily found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment. Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance stressors [@podsakoff2007differential]]. Interestingly, both challenges and hindrances have been shown to positively predict strain [(Abbas & Raja, 2019]@abbas2019challenge; @lepine2005meta; @podsakoff2007differential; @webster2010toward], which further highlights the complex association between appraisals and subsequent outcomes. Given the differential relationships described above, we make the following predictions:

@@

In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain [e.g., @bakker2005job] and burnout [e.g., @xanthopoulou2007job]. Bakker and colleagues (2005) were the first to report empirical evidence to support the idea job resources could potentially buffer the negative impact of job demands on stress reactions like burnout. @bakker2005job explored the interaction between 4 demands (e.g., work overload, physical demands) and 4 resources (e.g., social support, feedback) and three dimensions of burnout (exhaustion, cynicism, and professional efficacy), and found some support for the prediction that high demands with low resources predicted greater levels of cynicism and exhaustion among employees in higher education. Similarly, @xanthopoulou2007job also found some support for this interaction (high demands + low resources leads to greater burnout) among home healthcare employees. They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout. We extend the established job demands-resources model buffer proposition to both challenge and hindrance stressors (demands) as follows:

### 2024-07-10 Submission.tex
Updating the Introduction Section

Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing. Beginning with resources ADD JDR STUFF ON RESOURCES AND MOTIVATION HERE. Kim and Beehr (2020) found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a \emph{challenge} was associated with sources of motivation (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing. The opposite occurred when a demand was appraised as a \emph{hindrance} -- in those instances, the appraisal had a negative association with motivational resources. Cavanaugh et al. (2000), in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern. Chen et al. (2021) found that daily challenge demands were positively related to cognitive wellbeing and work-family enrichment. Daily hindrance demands were negatively related to these outcomes. In contrast, Abbas and Raja (2019) found that challenge and hindrance stressors were \emph{both} positively related to strain and turnover intentions. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with it (Crawford et al., 2010). Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety (Rodell \& Judge, 2009). Lastly, Gerich (2017) concluded that employee wellbeing was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands. In addition to the studies above, several meta-analyses also support differential associations across a variety of organizational outcomes as well. For example, both challenges and hindrances have been shown to positively predict strain (J. A. LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010). Many other outcomes are differentially related to challenges and hindrances, largely in the expected direction. For example, motivation, job satisfaction, commitment, and performance have been shown to positively relate to challenge stressors and negatively relate to hindrance stressors (J. A. LePine et al., 2005). Turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance stressors (Podsakoff et al., 2007). Kim and Beehr (2020), similarly, found evidence for the differential results via challenge and hindrance appraisals.

@@

In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain (e.g., Bakker et al., 2005) and burnout (e.g., Xanthopoulou et al., 2007). BUILD ON THIS - DETAILS OF THESE TWO STUDIES AND MORE - BAKKER 2010

@@

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-rodell2009can}{}}%
Rodell, J. B., \& Judge, T. A. (2009). Can {``good''} stressors spark {``bad''} behaviors? The mediating role of emotions in links of challenge and hindrance stressors with citizenship and counterproductive behaviors. \emph{Journal of Applied Psychology}, \emph{94}(6), 1438.

>>>>

Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance (e.g., J. A. LePine et al., 2005). We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout. Beginning with resources, Hakanen et al. (2008) found job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, Bakker et al. (2007) found that resources were most predictive of engagement when job demands were especially high.

The findings regarding demands are more complex, presumably because the way challenge vs.~hindrance appraisal influence coping strategies. Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and work meaningful (Chen et al., 2021), engagement (Crawford et al., 2010), and strain and turnover intentions (e.g., Abbas \& Raja, 2019), for example. Challenge appraisals have been negatively associated with job search behaviors (e.g., Cavanaugh et al., 2000).

Hindrance demands (appraisals) are largely related to outcomes as the job demands-resources model predicts. When a demand was appraised as a hindrance -- it was negatively associated with motivational resources (Kim \& Beehr, 2020), engagement (Crawford et al., 2010), job search behaviors and job satisfaction, (Cavanaugh et al., 2000). Chen et al. (2021) found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment. Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance stressors (Podsakoff et al., 2007){]}. Interestingly, both challenges and hindrances have been shown to positively predict strain ((Abbas \& Raja, 2019 Abbas \& Raja, 2019; J. A. LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010), which further highlights the complex association between appraisals and subsequent outcomes. Given the differential relationships described above, we make the following predictions:

@@

In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain (e.g., Bakker et al., 2005) and burnout (e.g., Xanthopoulou et al., 2007). Bakker and colleagues (2005) were the first to report empirical evidence to support the idea job resources could potentially buffer the negative impact of job demands on stress reactions like burnout. Bakker et al. (2005) explored the interaction between 4 demands (e.g., work overload, physical demands) and 4 resources (e.g., social support, feedback) and three dimensions of burnout (exhaustion, cynicism, and professional efficacy), and found some support for the prediction that high demands with low resources predicted greater levels of cynicism and exhaustion among employees in higher education. Similarly, Xanthopoulou et al. (2007) also found some support for this interaction (high demands + low resources leads to greater burnout) among home healthcare employees. They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout. We extend the established job demands-resources model buffer proposition to both challenge and hindrance stressors (demands) as follows:

@@

\leavevmode\vadjust pre{\hypertarget{ref-bakker2007job}{}}%
Bakker, A. B., Hakanen, J. J., Demerouti, E., \& Xanthopoulou, D. (2007). Job resources boost work engagement, particularly when job demands are high. \emph{Journal of Educational Psychology}, \emph{99}(2), 274.

@@

\leavevmode\vadjust pre{\hypertarget{ref-hakanen2008job}{}}%
Hakanen, J. J., Schaufeli, W. B., \& Ahola, K. (2008). The job demands-resources model: A three-year cross-lagged study of burnout, depression, commitment, and work engagement. \emph{Work \& Stress}, \emph{22}(3), 224--241.

@@
